---
title: "Solutions to Chapter 3 Exercises"
author: "Howard Baek"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
```


### 3.1.1 Exercises


1. What geoms would you use to draw each of the following named plots?

- Scatterplot: `geom_point()`
- Line chart: `geom_line()`
- Histogram: `geom_histogram()`
- Bar chart: `geom_bar()`
- Pie chart: ggplot2 does not have a geom to draw pie charts. One workaround, according to the [R Graph Gallery](https://www.r-graph-gallery.com/piechart-ggplot2.html) is to build a stacked bar chart with one bar only using the `geom_bar()` function and then make it circular with `coord_polar()`


2. What's the difference between `geom_path()` and `geom_polygon()`?

- `geom_polygon` draws the same graph (lines) as `geom_path`, but it fills these lines with color. See below:

```{r, include = FALSE}
df <- data.frame(
  x = c(3, 1, 5), 
  y = c(2, 4, 6), 
  label = c("a","b","c")
)
p <- ggplot(df, aes(x, y, label = label)) + 
  labs(x = NULL, y = NULL) + # Hide axis label
  theme(plot.title = element_text(size = 12)) # Shrink plot title
```


```{r, echo = FALSE}
p + 
  geom_path() +
  ggtitle("geom_path()")
```

```{r, echo = FALSE}
p + 
  geom_polygon() +
  ggtitle("geom_polygon()")
```


3. What's the difference between `geom_path()` and `geom_line()`

`geom_line()` connects points from left to right, whereas `geom_path()` connects points in the order they appear in the data. See below:

```{r, echo = FALSE}
p + 
  geom_line() +
  ggtitle("geom_line()")
```

```{r, echo = FALSE}
p + 
  geom_path() +
  ggtitle("geom_path()")
```


4. What low-level geoms are used to draw `geom_smooth()`? What about `geom_boxplot()` and `geom_violin()`? 

(kangnade) 

- `geom_point()`, `geom_path()`, and `geom_area()` are used to draw `geom_smooth()`.
- `geom_rect()`, `geom_line()`, `geom_point()` are used for `geom_boxplot()`.
- `geom_area()` and `geom_path()` are used for `geom_violin()`



