---
title: "Solutions to Chapter 19 Exercises"
author: "Howard Baek"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
```


### 19.2.1 Exercises

1. 
```{r}
pink_hist <- geom_histogram(
  color = "pink",
  bins = 100
)
```

2. 
```{r}
fill_blues <- scale_fill_distiller(
  palette = "Blues"
)
```


3.
```{r, eval=FALSE}
?theme_gray()
```

- Its arguments include `base_size`, `base_family`, `base_line_size`, and `base_rect_size`
- According to the help file, `theme_gray()` is the signature ggplot2 theme with a grey background and white gridlines and is designed to put the data forward yet make comparisons easy.



4.
```{r}
scale_colour_wesanderson <- function(palette = "BottleRocket1", ...) {
  scale_color_manual(values = wesanderson::wes_palette(palette), ...) 
}

# Working example
ggplot(mtcars, aes(wt, disp, color = factor(gear))) +
  geom_point() +
  scale_colour_wesanderson()
```




### 19.3.4 Exercises

1. 
```{r}
remove_labels <- theme(legend.position = "none",
                       axis.title.x = element_blank(),
                       axis.title.y = element_blank())

# Working Example
ggplot(mtcars, aes(wt, disp, color = factor(gear))) +
  geom_point() +
  remove_labels
```


2. Not sure 


### 19.4.3. Exercises

These questions are way above my head!

### 19.5.1 Exercises

These questions are way above my head!