---
title: "Solutions to Chapter 15 Exercises"
author: "Howard Baek"
date: "Last compiled on `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
```


### 15.1.1 Exercises

```{r}
####################################
####################################
# ggplot(mpg, aes(displ)) + 
#   scale_y_continuous("Highway mpg") + 
#   scale_x_continuous() +
#   geom_point(aes(y = hwy))

# The above can be modified to:
# mpg %>% 
#   ggplot(aes(displ, hwy)) +
#   geom_point() +
#   labs(y = "Highway mpg")
####################################
####################################




####################################
####################################
# ggplot(mpg, aes(y = displ, x = class)) + 
#   scale_y_continuous("Displacement (l)") + 
#   scale_x_discrete("Car type") +
#   scale_x_discrete("Type of car") + 
#   scale_colour_discrete() + 
#   geom_point(aes(colour = drv)) + 
#   scale_colour_discrete("Drive\ntrain")

# The above can be modified to
# mpg %>% 
#   ggplot(aes(class, displ)) +
#   geom_point(aes(color = drv)) +
#   labs(x = "Type of car",
#        y = "Displacement (l)",
#        color = "Drive\ntrain")
####################################
####################################
```




2. What happens if you pair a discrete variable with a continuous scale? What happens if you pair a continuous variable with a discrete scale?

```{r}
mpg %>%
  ggplot(aes(class, displ)) +
  geom_point(aes(color = drv)) +
  scale_y_discrete() +
  labs(x = "Type of car",
       y = "Displacement (l)",
       color = "Drive\ntrain")
```

- When you pair a discrete variable with a continuous scale, you don't see a plot and get this error message: _Discrete value supplied to continuous scale_

- When you pair a continuous variable with a discrete scale, as seen above, you get a different looking plot that doesn't contain the proper axis ticks or grid lines.


### 15.7 Exercises

According to the help pages,

- `name`: specifies the labels for **axis** and the title for **legends**.
- `breaks`: specifies the ticks and grid lines for **axis** and the key for **legends**.
- `labels`: specifies the tick label for **axis** and key label for **legends**.
